---
title: "Making it count: Improving primary school maths"
subtitle: "Analysis of Grattan Institute's survey of primary school teachers" 
date: "July 2024"
author: "Nick Parkinson"
format: 
  html:
    css: .formatting/grattan-style.css
    theme: lumen
    highlight: pygments
    toc: true
    toc_depth: 2
    number_sections: yes
    df_print: kable
    fig-cap-location: top
execute:
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: libraries
#| include: false

library(tidyverse)
library(grattantheme)
library(qualtRics)
library(knitr)
library(knitr)
library(kableExtra)
library(sjlabelled)
library(readxl)
library(janitor)
library(scales)
library(strayr)

# Additional configuration
options(knitr.kable.NA = '')
```

# Import data

We first import the data straight from Qualtrics following the instructions [here](https://api.qualtrics.com/instructions/ZG9jOjg3NjYzNQ-finding-your-qualtrics-i-ds). We also export a dated version of the survey, for file management.

```{r}
#| label: import
#| include: false

# To connect to the Qualtrics API, uncomment the following line of code the first time you run this  script, and then restart R.

# qualtrics_api_credentials(api_key = "yKIwTusJkJAY9esZ4GQkqZKURN7Pq1RxI6vkvD4Q", base_url = "melbourneuni.au1.qualtrics.com", install = TRUE)

surveys <- all_surveys()

survey_id <- surveys |>
  filter(str_detect(name, "primary school mathematics")) |>
  pull(id)

# Change the id below based on the id of the primary numeracy survey in your list of surveys.
raw_survey_data <- fetch_survey(
  surveyID = survey_id,
  verbose = FALSE,
  include_display_order = FALSE,
  start_date = as.Date("2024-07-04")
)

# Save the Qualtrics survey, just in case
currentDate <- Sys.Date()

filename <- paste("data/survey", currentDate, ".csv", set = "")

write.csv(raw_survey_data, file = filename)

# Check what data looks like
raw_survey_data |>
  select(matches("Q\\d+") & !contains(c("DO", "TEXT", "Q6", "Q7"))) |>
  head(5) |>
  kable() |>
  row_spec(0:5, extra_css = "height: 10px")
```

# Filter to valid sample

We filter out:

-   Anyone whose responses are [flagged by Qualtrics as suspicious](https://www.qualtrics.com/support/survey-platform/survey-module/survey-checker/fraud-detection/) (i.e. Q_RecaptchaScore is below 0.5). This is typically because of the speed at which they respond, or 'straight lining' (i.e. clicking the same radio buttons in a single column).

-   Anyone who did not complete more than one substantive (i.e. non-demographic) question.

```{r}
#| label: clean_survey

initial_sample <- nrow(raw_survey_data)

clean_survey <- raw_survey_data |>
  filter(Q_RecaptchaScore >= 0.5) # filter out bots

substantive_questions <- names(clean_survey)[which(names(clean_survey) == "Q24"):ncol(clean_survey) - 1]

# Check if all values in each row from Q24 onwards are NA
responses_to_keep <- rowSums(is.na(clean_survey[substantive_questions])) < length(substantive_questions)

clean_survey <- clean_survey[responses_to_keep, ]

total_sample <- nrow(clean_survey)
```

Through this process, we lose `r initial_sample - total_sample` responses. This leaves us with `r total_sample` valid responses.

We also check for duplicates, using [Qualtrics duplicate flag](https://www.qualtrics.com/support/survey-platform/survey-module/survey-checker/fraud-detection/). This pulls out respondents who try reattempt the survey from the same IP address. We can see if they are duplicates by looking through their answers manually.

```{r}
#| label: tab-check-for-duplicates
#| caption: Extract of data from possible duplicates

possible_duplicates <- clean_survey |>
  filter(Q_BallotBoxStuffing) |>
  select(ResponseId, IPAddress, matches("Q")) |>
  kable()
```

We now check the number of valid responses over time, in @fig-responses-over-time.

```{r}
#| label: fig-responses-over-time
#| fig-cap: "Number of responses over time"
clean_survey |>
  rowid_to_column() |>
  ggplot(aes(x = RecordedDate, y = rowid)) +
  geom_line() +
  theme_grattan() +
  scale_x_datetime(
    date_labels = "%d-%b",
    date_breaks = "day"
  ) +
  scale_y_continuous_grattan() +
  labs(x = NULL)
```

# Demographics

We create tables to determine the representativeness of the sample. We compare these again the latest available data [here](https://www.acara.edu.au/reporting/national-report-on-schooling-in-australia/staff-numbers#:~:text=Key%20Facts,schools%2018.2%25%20in%20independent%20schools.) and [here](https://www.acara.edu.au/reporting/national-report-on-schooling-in-australia/school-numbers).

## Teacher characteristics

```{r}
# label: tab-demographic-counts

# create custom function
demographic_counts <- function(column) {
  col_name <- sym(column)

  question_name <- get_label(clean_survey[[column]])

  clean_survey |> 
    count(!!col_name) |> 
    drop_na() %>%
    mutate(
      response = as.character(pull(., !!col_name)),
      prop = (n / sum(n)),
      demographic = str_extract(question_name, boundary("word")) |>
             str_to_sentence() |> str_replace_all("_", " ")) |> 
    select(demographic, response, n, prop)
}

# Read in ACARA staff data
acara_staff_data <- read_xlsx(path = "data/acara_staff_data.xlsx") |> 
  clean_names() |> 
  mutate(staff_count = parse_number(staff_count)) |> 
  filter(calendar_year == 2023)

# Sex
dem_sex <- demographic_counts("Q4") |>
  left_join(
    (acara_staff_data |>
      filter(
        state_territory == "Australia",
        school_sector == "All",
        school_level == "Primary",
        staff_function == "Teaching staff"
      ) |>
      group_by(sex_gender) |>
      summarise(n = sum(staff_count)) |>
      filter(sex_gender != "All") |>
      mutate(prop = (n / sum(n)))),
    by = join_by(response == sex_gender))

dem_sex |> 
  mutate(across(starts_with("prop"), percent, 1)) |> 
  select(-demographic) |> 
  kable(col.names = c("Response", "N", "%", "N", "%"), 
        align = c("lrrrr"), 
        digits = 0, 
        format.args = list(big.mark = ',')) |> 
    add_header_above(c("Characteristic" = 1, "Grattan survey" = 2, "Population data" = 2))

# Role

# Years of experience

```

## School characteristics

```{r}
# Read in ACARA school profile dataset
# Source: https://view.officeapps.live.com/op/view.aspx?src=https%3A%2F%2Fdataandreporting.blob.core.windows.net%2Fanrdataportal%2FData-Access-Program%2FSchool%2520Profile%25202023.xlsx&wdOrigin=BROWSELINK

acara_school_data <- read_excel("data/acara_school_profile.xlsx", sheet = 2) |> 
  clean_names()

# School type
school_type_school_profile <- acara_school_data |> 
  group_by(school_type) |> 
  summarise(n = sum(teaching_staff, na.rm = T)) |> 
  mutate(prop = n/sum(n))

school_type_staff_data <- acara_staff_data |> 
  filter(state_territory == "Australia", 
         school_sector == "All", 
         sex_gender == "All",
         staff_function == "Teaching staff") |> 
  group_by(school_level) |> 
  summarise(n = sum(staff_count)) |> 
  mutate(prop = n/sum(n))

combined_in_primary <- 
  (school_type_school_profile |> 
  filter(school_type == "Combined") |> 
  pull(n)) - (school_type_staff_data$n[2] - school_type_school_profile$n[2] - school_type_school_profile$n[4]/2) # Assume that half of all teachers in special schools work with primary aged kids

# Determine how many of the combined and special staff work in primaries
school_type_australia <- 
  school_type_school_profile |> 
  mutate(n = case_when(
    school_type == "Combined" ~ combined_in_primary,
    school_type == "Special" ~ n/2, 
    .default = n)) |> 
  filter(school_type %in% c("Primary", "Combined", "Special"))

school_type_survey <- clean_survey |> 
  mutate(school_type =  case_when(
    Q16 == "Yes" ~ "Special",
    Q3 == "Primary" ~ "Primary", 
    Q3 == "Combined primary and secondary" ~ "Combined"
  )) |> 
  count(school_type) |> 
  drop_na() |> 
  mutate(prop = n/sum(n))

school_type <- left_join(school_type_survey, 
                         school_type_australia, 
                         by = join_by(school_type == school_type)) |> 
  arrange(-n.x) |> 
  rename(response = school_type)

rm(school_type_australia, school_type_school_profile, school_type_staff_data, school_type_survey)

# School sector
school_sector <- left_join(
demographic_counts("Q18"),
  (acara_staff_data |> 
  filter(state_territory == "Australia", 
         school_level == "Primary",
         staff_function == "Teaching staff",
         sex_gender == "All") |> 
  group_by(school_sector) |> 
  summarise(n = sum(staff_count)) |> 
  filter(school_sector != c("All", "All non-government")) |> 
  mutate(prop = n/sum(n))),
by = join_by(response == school_sector)) |> 
  select(-demographic)

# State and territory 
state_and_territory <- 
  left_join(
  (demographic_counts("Q19") |> 
  mutate(response = clean_state(response, to = "state_name"))),
  (acara_staff_data |>
    filter(
      school_sector == "All",
      school_level == "Primary",
      staff_function == "Teaching staff",
      sex_gender == "All"
    ) |>
    group_by(state_territory) |>
    summarise(n = sum(staff_count)) |>
    filter(state_territory != "Australia") |>
    mutate(prop = n / sum(n))),
  by = join_by(response == state_territory)
) |> 
  select(-demographic)

# Advantage
ses <-  
  left_join(
    demographic_counts("Q20"),
  (acara_school_data |> 
  mutate(ses = case_when(
    icsea_percentile <= 33.33 ~ "Mostly disadvantaged",
    between(icsea_percentile, 33.33, 66.66) ~ "A fairly even mix of advantaged and disadvantaged students",
    icsea_percentile >= 66.66 ~ "Mostly advantaged"
  )) |> 
  group_by(ses) |> 
  summarise(n = sum(teaching_staff, na.rm = T)) |> 
  drop_na() |> # Some NAs for schools without ICSEA values
  mutate(prop = n/sum(n))),
  by = join_by(response == ses)) |> 
  select(-demographic)

# Location
location <- 
  left_join(
    demographic_counts("Q21"),
  (
  acara_school_data |> 
  mutate(simplified_geography = case_when(
    geolocation == "Major Cities" ~ "Metropolitan",
    geolocation == "Inner Regional" ~ "Regional", 
    geolocation == "Outer Regional" ~ "Rural",
    geolocation == "Remote" ~ "Remote", 
    geolocation == "Very Remote" ~ "Remote"
  )) |> 
  group_by(simplified_geography) |> 
  summarise(n = sum(teaching_staff, na.rm = T)) |> 
  mutate(prop = n/sum(n))),
  by = join_by(response == simplified_geography)) |> 
  select(-demographic)

# School size
school_size_survey <- 
  clean_survey |> 
  count(Q22) |> 
  drop_na() |> 
  mutate(prop = n/sum(n))

school_size_australia <- 
  acara_school_data |> 
  # What to do about special and combined?
  filter(school_type == "Primary") |> 
  mutate(size = case_when(
     is.na(total_enrolments) ~ NA_character_, 
    total_enrolments <= 50 ~ "Up to 50 students",
    total_enrolments > 50 & total_enrolments <= 100 ~ "51 to 100 students",
    total_enrolments > 100 & total_enrolments <= 200 ~ "101 to 200 students",
    total_enrolments > 200 & total_enrolments <= 300 ~ "201 to 300 students",
    total_enrolments > 300 & total_enrolments <= 400 ~ "301 to 400 students",
    total_enrolments > 400 & total_enrolments <= 500 ~ "401 to 500 students",
    total_enrolments > 500 & total_enrolments <= 600 ~ "501 to 600 students",
    total_enrolments > 600 & total_enrolments <= 700 ~ "601 to 700 students",
    total_enrolments > 700 & total_enrolments <= 800 ~ "701 to 800 students",
    total_enrolments > 800 & total_enrolments <= 900 ~ "801 to 900 students",
    total_enrolments > 900 & total_enrolments <= 1000 ~ "901 to 1000 students",
    total_enrolments > 1000 ~ "More than 1,000 students"
  )) %>%
  group_by(size) |> 
  summarise(n = sum(teaching_staff, na.rm = T)) |> 
  drop_na() |> 
  mutate(prop = n/sum(n))

school_size <- 
  left_join(
  school_size_survey, 
  school_size_australia, 
  by = join_by(Q22 == size)
) |>  
  mutate(Q22 = factor(Q22, levels = c(
    "Up to 50 students",
    "51 to 100 students",
    "101 to 200 students",
    "201 to 300 students",
    "301 to 400 students",
    "401 to 500 students",
    "501 to 600 students",
    "601 to 700 students",
    "701 to 800 students",
    "801 to 900 students",
    "901 to 1000 students",
    "More than 1,000 students"
  ))) |> 
  arrange(Q22) |> 
  rename(response = Q22)

# Print table

rbind(school_type,
      school_sector,
      state_and_territory,
      ses,
      location,
      school_size) |> 
  mutate(across(starts_with("prop"), percent, 1)) |> 
  kable(col.names = c("Response", "N", "%", "N", "%"), 
        align = c("lrrrr"), digits = 0, 
        format.args = list(big.mark = ',')) |> 
  add_header_above(c("Characteristic" = 1, "Grattan survey" = 2, "Population data" = 2)) |> 
  pack_rows("Stage of schooling", 1, 3, color = grattan_orange) |> 
  pack_rows("Sector", 4, 6, color = grattan_orange) |> 
  pack_rows("Jursidiction", 7, 14, color = grattan_orange) |> 
  pack_rows("Level of advantage or disadvantage", 15, 17, color = grattan_orange) |> 
  pack_rows("Remoteness", 18, 21, color = grattan_orange) |> 
  pack_rows("School size", 22, 33, color = grattan_orange)

  
```

\
\
